\section{Problem}

\paragraph{}{
	GCom is a middle ware for group communication. It means,
 GCom has to be scallable and robust.
}

\subsection{Requirements}

\paragraph{Scalability}{
	To be scallable, GCom uses Peer to Peer based features.
 Typically, data is not centralized on a server but shared 
 between the nodes within groups. The implementation of the
 middleware uses Java programming language and Java RMI API to
 ensure portability over different operation systems.
}

\paragraph{Transparency}{
	The front end user, or the programmer who will use our
 library, GCom should be seen as a service they can use to
 exchange messages between several computer regardless the
 type of the used networks or the type of the application.
 GCom must offer a simple interface and hide how, for
 instance, messages are delivered.
}

\paragraph{Openness}{
	GCom must be designed to be extensible. Adding or changing 
 components should not be a problem. for instance, using a FIFO
 or a causal order for messages delivering should interface or
 compromise the whole application.
}

\paragraph{Quality of Service (QoS)}{
	If one or several nodes failed, the other nodes must keep
 working and processing data. In the same way as, If a part of
 the network is down, remaining nodes must work.
}

\subsection{Efficiency and fault tolerance}

\paragraph{}{
	GCom is a middleware, so to be useful, GCom must process
 data and handle common errors quickly. Regardless the number 
 of connected nodes in a group, adding or removing members within
 the group as well as electing a new leader must be done
 quickly and don't be noticed by front-end users.
}

\paragraph{}{
	When nodes fail, every node must be notified that a node
 is down and should no more be reached. As well, for new nodes,
 every nodes should know when a new node joined the group. The
 same strategy must be applied for leaders. When a new leader is
 elected, every group members must be notified and considering
 the new leader. Finally, when a leader is down, a new one must
 be elected only by the group members.
}

\paragraph{}{
	Several questions must be solved during the application
 development. For instance, how elect a new leader? How often?
 What happen when the group is cut into pieces (because of a
 network failure) and then the network is once again reliable?
}
